---
title: "Test 1 - Positions"
author: "Yoni Slutzky"
date: "5/15/2021"
output: html_document
---

## Load files
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load files
```{r}
path2 <- "C:/Users/GIGABAYT/Desktop/projectstat/CSVs/P2P_Comma.csv"
p2p <- read.delim(file = "C:/Users/GIGABAYT/Desktop/projectstat/CSVs/P2P_Comma.csv", header = TRUE, sep = ",")
knsts <- read.delim(file = "C:/Users/GIGABAYT/Desktop/projectstat/CSVs/Knessets_Comma.csv", header = TRUE, sep = ",")

#p2p <- read.delim(file = "D:/Studies/Year A Sem B/Intro to Statistics/Project/P2P_Comma.csv", #header = TRUE, sep = ",")
#knsts <- read.delim(file = "D:/Studies/Year A Sem B/Intro to #Statistics/Project/Knessets_Comma.csv", header = TRUE, sep = ",")
```

## Clean P2P
```{r}
ord <- order(p2p$PersonID)
p2p <- p2p[ord, ]
CleanP2P <- function(kns){
  # Returns a p2p without non-mks, and without duplicates for Knesset kns
  cleaned_indices <- !is.na(p2p$FactionID) & (p2p$KnessetNum == as.character(kns))
  cleaned <- p2p[cleaned_indices,]
  fixed_indices <- !(duplicated(cleaned$PersonID))
  fixed <- cleaned[fixed_indices,]
  fixed
}
```

## Get factions IDs in kns
```{r}
factions_in_kns <- function(kns_num, small = FALSE) {
  #Returns FactionIDs during given kns
  if (small){
    knsts$Faction.ID[knsts$Knesset == kns_num & knsts$Mandates <= 7]
  }
  else {
    knsts$Faction.ID[knsts$Knesset == kns_num]
  }
}
```

## Persons in faction in kns
```{r}
faction_persons <- function(faction_id, kns_num) {
  #Returns PersonsIDs in a given faction during given kns
  cleaned_indices <- (p2p$UpdatedFactionID == as.character(faction_id) & p2p$KnessetNum == as.character(kns_num))
  cleaned_indices <- ifelse(is.na(cleaned_indices) | cleaned_indices == FALSE, FALSE, TRUE)
  right_kns <- p2p[cleaned_indices,]
  unique(right_kns$PersonID)
}
```

## Positions for a given faction and a given kns
```{r}
faction_positions <- function(faction_id, kns_num) {
  #Returns positions for a given faction during a given kns
  persons <- faction_persons(faction_id, kns_num)
  positions <- c()
  for (person in persons) {
    positions <- append(positions, p2p$PositionID[p2p$PersonID == as.character(person) 
                                                  & p2p$KnessetNum == as.character(kns_num)])
  }
  positions
}
```

## Filter important positions for a given faction during given kns
```{r}
faction_relevant_positions <- function(faction_id, relevant_positions, kns_num) {
  #Filters relevant positions for a given faction during given kns
  faction_positions <- faction_positions(faction_id, kns_num)
  faction_positions[faction_positions %in% relevant_positions]
}
```

## Create vectors of proportions of positions for small factions for early and later knsts
```{r}
relevant_positions <- c(29, 30, 31, 39, 40, 41, 42, 49, 50, 51, 57, 59, 65, 70, 
                        71, 73, 122, 123, 130, 131, 285078)
total_positions <- rep(0, 24)
small_faction_positions <- rep(0, 24)
for (i in 1:24) {
  factions <- factions_in_kns(i)
  for (item in factions) {
    total_positions[i] <- total_positions[i] + 
      length(faction_relevant_positions(item, relevant_positions, i))
  }
  small_factions <- factions_in_kns(i, TRUE)
  for (item in small_factions) {
    small_faction_positions[i] <- small_faction_positions[i] + 
      length(faction_relevant_positions(item, relevant_positions, i))
  }
}
later_knsts_props <- (small_faction_positions/total_positions)[21:24]
early_knsts_props <- (small_faction_positions/total_positions)[1:20]
```

## Boxplots of proportions in early and later knsts
```{r}
mat <- cbind("Early Knessets" = early_knsts_props, "Late Knessets" = later_knsts_props)
boxplot(mat, main = "התפלגות פרופורציית התפקידים של גוש המפלגות הקטנות (1)", ylab = "Proportions", )
#points(c(mean(early_knsts_props),mean(later_knsts_props)), pch = 2, col = 2)
```


## Wilcoxon rank sum test
```{r}
wilcox.test(x = later_knsts_props, y = early_knsts_props, alternative = "greater", exact = TRUE, 
            correct = FALSE, conf.int = TRUE)


all_permutations <- combn(rank(c(early_knsts_props, later_knsts_props)), 4)
w_null3 <- apply(all_permutations, 2, sum)
qqnorm(w_null3, main = "Normal Q-Q Plot - Test 1")
```

## Plot empiric proportions
```{r}
plot(small_faction_positions/total_positions, xaxt = 'n', main = "Empiric proportions per Knesset",
     xlab = "Knesset", ylab = "Proportion of positions for smalls",
     col = c(rep(1,20), rep(2,4)))
axis(1, at = 1:24, las = 2)
```



