---
title: "Tests Data"
author: "me"
date: "31 5 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Tests 1 - Small Factions Bloc positions proportion in Knesset

**An important notion - 'Small Factions Bloc': The Group of all Knesset members who are identified with a small sized party (7 mandates or less).**

#### Load files
```{r}

p2p <- read.delim(file = "TestsFiles/P2P_Comma.csv", header = TRUE, sep = ",")
knsts <- read.delim(file = "TestsFiles/Knessets_Comma.csv", header = TRUE, sep = ",")

```

#### Clean P2P
```{r}
ord <- order(p2p$PersonID)
p2p <- p2p[ord, ]
CleanP2P <- function(kns){
  # Returns a p2p without non-mks, and without duplicates for Knesset kns
  cleaned_indices <- !is.na(p2p$FactionID) & (p2p$KnessetNum == as.character(kns))
  cleaned <- p2p[cleaned_indices,]
  fixed_indices <- !(duplicated(cleaned$PersonID))
  fixed <- cleaned[fixed_indices,]
  fixed
}
```

#### Get factions IDs in kns
```{r}
factions_in_kns <- function(kns_num, small = FALSE) {
  #Returns FactionIDs during given kns
  if (small){
    knsts$Faction.ID[knsts$Knesset == kns_num & knsts$Mandates <= 7]
  }
  else {
    knsts$Faction.ID[knsts$Knesset == kns_num]
  }
}
```

#### Persons in faction in kns
```{r}
faction_persons <- function(faction_id, kns_num) {
  #Returns PersonsIDs in a given faction during given kns
  cleaned_indices <- (p2p$UpdatedFactionID == as.character(faction_id) & p2p$KnessetNum == as.character(kns_num))
  cleaned_indices <- ifelse(is.na(cleaned_indices) | cleaned_indices == FALSE, FALSE, TRUE)
  right_kns <- p2p[cleaned_indices,]
  unique(right_kns$PersonID)
}
```

#### Positions for a given faction and a given kns
```{r}
faction_positions <- function(faction_id, kns_num) {
  #Returns positions for a given faction during a given kns
  persons <- faction_persons(faction_id, kns_num)
  positions <- c()
  for (person in persons) {
    positions <- append(positions, p2p$PositionID[p2p$PersonID == as.character(person) 
                                                  & p2p$KnessetNum == as.character(kns_num)])
  }
  positions
}
```

#### Filter important positions for a given faction during given kns
```{r}
faction_relevant_positions <- function(faction_id, relevant_positions, kns_num) {
  #Filters relevant positions for a given faction during given kns
  faction_positions <- faction_positions(faction_id, kns_num)
  faction_positions[faction_positions %in% relevant_positions]
}
```

#### Create vectors of proportions of positions for small factions for early and later knsts
```{r}
relevant_positions <- c(29, 30, 31, 39, 40, 41, 42, 49, 50, 51, 57, 59, 65, 70, 
                        71, 73, 122, 123, 130, 131, 285078)
total_positions <- rep(0, 24)
small_faction_positions <- rep(0, 24)
for (i in 1:24) {
  factions <- factions_in_kns(i)
  for (item in factions) {
    total_positions[i] <- total_positions[i] + 
      length(faction_relevant_positions(item, relevant_positions, i))
  }
  small_factions <- factions_in_kns(i, TRUE)
  for (item in small_factions) {
    small_faction_positions[i] <- small_faction_positions[i] + 
      length(faction_relevant_positions(item, relevant_positions, i))
  }
}
later_knsts_props <- (small_faction_positions/total_positions)[21:24]
early_knsts_props <- (small_faction_positions/total_positions)[1:20]
```

#### Boxplots of proportions in early and later knsts
```{r}
mat <- cbind("Early Knessets" = early_knsts_props, "Late Knessets" = later_knsts_props)
boxplot(mat, main = "התפלגות פרופורציית התפקידים של גוש המפלגות הקטנות (1)", ylab = "Proportions", )
#points(c(mean(early_knsts_props),mean(later_knsts_props)), pch = 2, col = 2)
```


#### Wilcoxon rank sum test
```{r}
wilcox.test(x = later_knsts_props, y = early_knsts_props, alternative = "greater", exact = TRUE, 
            correct = FALSE, conf.int = TRUE)


all_permutations <- combn(rank(c(early_knsts_props, later_knsts_props)), 4)
w_null3 <- apply(all_permutations, 2, sum)
qqnorm(w_null3, main = "Normal Q-Q Plot - Test 1")
```

#### Plot empiric proportions
```{r}
plot(small_faction_positions/total_positions, xaxt = 'n', main = "Empiric proportions per Knesset",
     xlab = "Knesset", ylab = "Proportion of positions for smalls",
     col = c(rep(1,20), rep(2,4)))
axis(1, at = 1:24, las = 2)
```



\newpage


## Tests 2 & 3

```{r}
path2 <- "TestsFiles/Knessets.csv"
Knessets <- read.delim(file = path2, header=TRUE, sep = ',')

# Calculates the size of Knesset members in Coalition, among Small Factions,
# in the specified Knesset number.
# Small Factions defined to be factions with 7 mandates or less.
smallInCoalition_PartiesSize <- function(kns.num){
  A <- Knessets[Knessets$Knesset == kns.num, ]
  x <- A$SmallParty == 'V' & A$Coalition == 'V'
  sum(A$Mandates[x])
}

# Calculates the size of Knesset members in *Knesset*, among Small Factions,
# in the specified Knesset number.
# Small Factions defined to be factions with 7 mandates or less.
smallInKneset <- function(kns.num){
  A <- Knessets[Knessets$Knesset == kns.num, ]
  x <- A$SmallParty == 'V'
  sum(A$Mandates[x])
}


smallCount_InCoalition <- sapply(c(1:24), smallInCoalition_PartiesSize)

smallCount_InKnesset <- sapply(c(1:24), smallInKneset)

smallRate_OutOfCoalition <- smallCount_InCoalition / smallCount_InKnesset

```


\

\newpage

## Test 2 - Small Factions Bloc size


#### Boxplots of proportions in early and later knsts
\
```{r}
boxplot(smallCount_InKnesset[1:20],
        smallCount_InKnesset[21:24],
        main = 'התפלגות מספר חברי המפלגות הקטנות מתוך הכנסת (2)', ylab = 'Knesset Members',
        names = c("Eearly Knessets", "Late Knessets"))
```

\

\newpage


```{r}
plot(smallCount_InKnesset, xlab = 'Knessets', 
                      ylab = 'Small Factions in size in Knesset')


resid <- lm(smallCount_InKnesset ~ c(1:24))
abline(resid, col = 'yellow')
```

```{r, fig.width=3, fig.height=3}
plot(resid$residuals ~ c(1:24), main = "Residuals Plot of Test 2")
abline(0,0)
```

\newpage

####Wilcoxon Rank Sum test for size mean:
```{r}
kns_1.to.20 <- smallCount_InKnesset[1:20]
kns_21.to.24 <- smallCount_InKnesset[21:24]

wilcox.test(x = kns_1.to.20, y = kns_21.to.24, alternative = "less",
            mu = 0, conf.level = 0.95, exact = F)


all_permutations<- combn(rank(c(kns_1.to.20, kns_21.to.24)), 4)
w_null2 <- apply(all_permutations, 2, sum)
qqnorm(w_null2, main = "Normal Q-Q Plot - Test 2")
```

\

\newpage

## Test 3 - Rate between Knesset members in Coalition, out of the Small Factions Bloc, to Knesset members in General


\

```{r}
coalitionSize <- function(kns.num){
  A <- Knessets[Knessets$Knesset == kns.num, ]
  x <- A$Coalition == 'V'
  sum(A$Mandates[x])
}

coalition_Sizes <- sapply(c(1:24), coalitionSize)

smallRate_New <- smallCount_InCoalition / coalition_Sizes
```

\

\newpage

#### Boxplots of proportions in early and later knsts

```{r}
boxplot(smallRate_New[1:20], smallRate_New[21:24],
        main = 'התפלגות פרופורציית גודל המפלגות הקטנות מתוך הקואליציה (3)',
        names = c("Early Knessets", "Late Knessets"), ylab ='Proportions')
#points(c(mean(smallRate_New[1:20]),mean(smallRate_New[21:24])), pch = 2, col = 2)
```

\

\newpage

```{r}
plot(smallRate_New ~ c(1:24), xlab = 'Knessets', 
                      ylab = 'Rate')


resid <- lm(smallRate_New ~ c(1:24))
abline(resid, col = 'yellow')
```

```{r, fig.width=3, fig.height=3}
plot(resid$residuals ~ c(1:24), main = "Residuals Plot of Test 3")
abline(0,0)
```

\newpage

####Wilcoxon Rank Sum test for proportion diff:
```{r}
kns_1.to.20 <- smallRate_New[1:20]
kns_21.to.24 <- smallRate_New[21:24]

wilcox.test(x = kns_1.to.20, y = kns_21.to.24, alternative = "less",
            mu = 0, conf.level = 0.95, exact = F)

all_permutations <- combn(rank(c(kns_1.to.20, kns_21.to.24)), 4)
w_null3 <- apply(all_permutations, 2, sum)
qqnorm(w_null3, main = "Normal Q-Q Plot - Test 3")
```
